An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-09-29 paper.tex
Update §5.2.4

We also look at the top 20\% participants from the co-authorship network
who are \emph{not} part of the top 20\% influencers in the email network in
Figure \ref{fig:non_overlapping_coauthornetwork_authors_emailnetwork}.
We observe that that are some prolific authors are that \emph{not} engaged
in the email discussion: 40\%-50\% of non-overlapping authors are ranked
between 20th to 40th percentile of influence in the email network. These
non-overlapping authors are typically more junior with respect to their
participation duration.

@@

We conclude that the IETF is still reasonably centralised, but that this
has improved over the years. However, removing around 20\%-25\% most
influential participants still fragments the entire network
(\S\ref{subsec:measuring_influence}, Figure
\ref{fig:purge_nodes_largest_connected_component_number_components}). The
most influential people are the ones with highest degree of engagements
within the community who also tend to be more involved in draft authoring
activities (\S\ref{subsec:influencer_behaviour}, Figure
\ref{fig:drafts_initiation_top_percentile}). However, we also observe that
over the years more people (even the ones less influential in the email
network) are getting involved in draft authoring activities (Figure
\ref{fig:drafts_initiation_top_percentile}). This shows that these
activities, while centralised to a certain degree, are still open to
contributions from the wider IETF community.

@@

A considerable portion of influential participants ($\sim$30\%) are
affiliated to one of the more prominent organisations (e.g., \emph{Cisco}
or \emph{Ericsson}) (\S\ref{subsec:impact_influence}, Figure
\ref{fig:coauthor_affiliation_network2019_otheryears}). Participants from
different organisations do considerably collaborate (Figure
\ref{fig:heatmap_2019_coauthordraft_most_frequent_org}). Moreover, the
level of such collaboration is found to have increased with time.

>>>>

We also look at the top 20\% participants from the co-authorship network
who are \emph{not} part of the top 20\% influencers in the email network in
Figure \ref{fig:non_overlapping_coauthornetwork_authors_emailnetwork}.
We observe that some prolific authors are \emph{not} engaged
in the email discussion: 40\%-50\% of non-overlapping authors are ranked
between 20th to 40th percentile of influence in the email network. These
non-overlapping authors are typically more junior with respect to their
participation duration.

@@

The IETF is a reasonably centralised organisation, that dominated by a
relatively small group of influential participants, but this dominance
is gradually reducing over time.
However, removing around 20\%-25\% most influential participants still
fragments the email graph (\S\ref{subsec:measuring_influence}, Figure
\ref{fig:purge_nodes_largest_connected_component_number_components}).

The most influential participants are those with the highest degree of
engagement within the community. These also tend to be more involved in
draft authoring (\S\ref{subsec:influencer_behaviour}, Figure
\ref{fig:drafts_initiation_top_percentile}). However, we also observe that
over the years more people, even those less influential in the email
network, are getting involved in draft authoring activities (Figure
\ref{fig:drafts_initiation_top_percentile}). This shows that these
activities, while centralised to a certain degree, are still open to
contributions from the wider IETF community.

@@

Finally, a considerable portion of influential participants ($\sim$30\%)
are affiliated with one of the more prominent organisations, e.g., Cisco
or Ericsson, (Figure \ref{fig:coauthor_affiliation_network2019_otheryears}).
Participants from different organisations do considerably collaborate
(Figure \ref{fig:heatmap_2019_coauthordraft_most_frequent_org}). Moreover,
the level of such collaboration is found to have increased with time.
